### 2014-04-14 doc/uist14/interaction.tex
update interactino tex
refined interaction and added comments

In this section, we first describe how head orientation-based interaction works from the users' point of view (Figure~\ref{fig:intearaction}).

{\bf Scan:} The user first scans the environment to locate the position of the target. During this stage, Glass will constantly sends out IR signal, and the target offers immediate feedback when it receives the IR.

{\bf Coarse Selection:} The user confirms his desire to connect to a target by tapping on the Glass touchpad. At this time, Glass collects the replies from targets about the IR signal reception. If there is only a single target in IR range, then it's considered as a successful selection. However, in a relative dense environment where multiple targets are within range, the user needs to perform a fine selection.

{\bf Fine selection:} When disambiguation is needed, the user needs to make an explicit selection among the targets that within his view range. There are multiple ways to achieve it -- either from Glass touchpad that controls a UI list or using the head motion sensor on Glass. We will leave a thorough and complete discussion later. Once the user confirms the current selection, he could tap to complete the acquisition. Since this part is effectively disambiguate among potential targets, we will also use {\em disambiguation} to refer to this stage.

>>>>

In this section, we describe how head orientation-based interaction works from the users' point of views (Figure~\ref{fig:interaction}). \sean{do we want to just use the term Glass or explains that it stands for any head-worn computing devices?}

{\bf Scan:} The user first scans the environment to locate the position of the target. During this stage, Glass constantly sends out IR signals, and the target offers immediate feedback when it receives the signal.

{\bf Coarse Selection:} The user confirms his desire to connect to a target by tapping on the Glass touchpad. Glass collects the responses from targets regarding their IR signal reception. If there is only one single target in IR range, then it's automatically connected and the selection process is completed. However, in a relative dense environment where multiple targets are within range, the user needs to perform a fine selection.

{\bf Fine selection:} When disambiguation is needed, the user needs to make an explicit selection among the targets that within his view range. There are multiple ways to achieve it -- either from Glass touchpad that controls a GUI list or using the head motion sensor on Glass. We will provide a thorough and complete discussion later in the paper. Once the user confirms the current selection, he could tap to complete the fine selection process. Since the purpose of this stage is to effectively disambiguate among potential targets, we will also use {\em disambiguation} to refer to this stage.

### 2014-04-14 doc/uist14/intro.tex
refined interaction and added comments

%% from the swarm vision to the necessity of selection
The number of smart objects with computation and communication powers have grown rapidly in the past years. Therefore, potential interactive targets in our environment has also increased.
%Such interactions might be {\em explicit} -- controlling smart appliances such as intelligent lighting, AV equipment, or HVAC systems; or {\em implicit} -- tracking the user's attention to gauge interest e.g., for targeted-advertisement or context-aware computing \bjoern{second part needs to be stronger}. 
To initiate such interaction requires {\em selection} information by which a system keeps track of the user's {\em locus of attention}~\cite{raskin} in the world. \sean{this sentence is unclear.}

%% previous approaches are limited
Past research has introduced techniques of augmenting hand-held mobile devices with accessories like laser pointers to enable direct aiming at target devices in space~\cite{beigl_point_1999,patel_2-way_2003}. While promising, some drawbacks of using hand-held devices are that the device first has to be retrieved (e.g., from a pocket) and consciously \sean{or do you mean cautiously?} aimed; that the user's hands are required to be free for operation (one to hold the device, one to operate the touch screen or keyboard); and that the user's visual attention is split between looking down at a screen and out at targets in the world.

>>>>

%% from the swarm vision to the necessity of selection
The number of smart objects with computation and communication powers have grown rapidly in the past years. Therefore, potential interactive targets in our environment has also increased.
%Such interactions might be {\em explicit} -- controlling smart appliances such as intelligent lighting, AV equipment, or HVAC systems; or {\em implicit} -- tracking the user's attention to gauge interest e.g., for targeted-advertisement or context-aware computing \bjoern{second part needs to be stronger}. 
To initiate such interaction requires {\em selection} information by which a system keeps track of the user's {\em locus of attention}~\cite{raskin} in the world. \sean{this sentence is unclear to me.}

%% previous approaches are limited
Past research has introduced techniques of augmenting hand-held mobile devices with accessories like laser pointers to enable direct aiming at target devices in space~\cite{beigl_point_1999,patel_2-way_2003}. While promising, some drawbacks of using hand-held devices are that the device first has to be retrieved (e.g., from a pocket) and consciously aimed; that the user's hands are required to be free for operation (one to hold the device, one to operate the touch screen or keyboard); and that the user's visual attention is split between looking down at a screen and out at targets in the world.
